HUME: Human UCCA-based Machine-Translation Evaluation

### 2016-03-08 paper/main.tex
a bit about the system

@@

>>>>

For each of the four language pairs under consideration (i.e. English to 
Czech, German, Polish and Romanian) we built phrase-based MT systems
using Moses \cite{Koehn:2007}. We used large training sets extracted from OPUS \cite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \cite{bojar-EtAl:2014:W14-33}, to provide between
45 and 85 million sentences of training data, depending on language pair.

These translation systems were used to translate texts derived from both NHS 24\footnote{\url{http://www.nhs24.com/}} and 
Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages. The first organisation is a public body
providing healthcare and health-service related information in Scotland, whereas the second is an international NGO which 
provides independent systematic reviews on health-related research. From NHS 24, we selected the segments from their
``Health A-Z'' which is part of the NHS Inform website, and the Cochrane texts come from their plain language summaries
and abstracts.\bh{How much more do we need? Perhaps in the intro we could justify our focus on public health text
(accuracy!). The test corpora should have a public URL by the time we submit, although of course the source texts were 
already public anyway, and Lexi did some selection of examples for use in this expt. -- do we have to explain this?}

@@

For the annotation process, we recruited seven annotators, two for each of the target languages apart from Czech. They were
all native speakers of the target languages and fluent in English. For Czech, we also recruited a  group of additional annotators
to annotate small numbers of sentences each for the purpose of calculating inter-annotator agreement. In \tabref{tab:annot}
we show the total number of sentences and nodes annotated by each annotator, where we consider the additional Czech
annotators as a single annotator.
